--- 
title: "Homework2"
author: "Jieying Jiao"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is Jieying's homework 2, Fall 2018"
---

# Exercise 1.2

```{r eval=FALSE, echo = FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

## Use Monte Carlo to estimate $\Phi(t)$

The Monte Carlo methods gives:

$$\hat{\Phi}(t) = \frac{1}{n}\sum_{i = 1}^nI(X_i\leqslant t)$$
where $X_i$ are random normal sample drawn from $N(0, 1)$.

```{r homework2_1}
library(xtable)
phi.MC <- function(n, t) {
  phi.hat <- matrix(0, nrow = length(n), ncol = length(t))
  for (i in 1:length(n)) {
    for (j in 1:length(t)) {
      X <- rnorm(n[i], 0, 1)
      phi.hat[i, j] <- mean(as.numeric(X <= t[j]))
    }
  }
truth <- pnorm(t)
phi.hat <- rbind(phi.hat, truth)
}
n <- c(10^2, 10^3, 10^4)
t <- c(0.0, 0.67, 0.84, 1.28, 1.65, 2.32, 2.58, 3.09, 3.72)
set.seed(1)
phi.hat <- phi.MC(n, t)
rownames(phi.hat) <- c(paste0("n = 10e", 2:4), "truth")
colnames(phi.hat) <- paste0("t = ", t)
t.MC <- xtable(phi.hat, digits = 4, caption = "Monte Carlo estimation", label = "MC result")
```

The estimation results are shown in Table \ref{MC result}.
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrrr}
  \hline
 & t = 0 & t = 0.67 & t = 0.84 & t = 1.28 & t = 1.65 & t = 2.32 & t = 2.58 & t = 3.09 & t = 3.72 \\ 
  \hline
n = 10e2 & 0.4600 & 0.7700 & 0.7800 & 0.8700 & 0.9200 & 1.0000 & 0.9900 & 1.0000 & 1.0000 \\ 
  n = 10e3 & 0.5110 & 0.7370 & 0.7710 & 0.9080 & 0.9500 & 0.9860 & 0.9990 & 0.9980 & 1.0000 \\ 
  n = 10e4 & 0.5061 & 0.7467 & 0.8021 & 0.8981 & 0.9527 & 0.9913 & 0.9947 & 0.9985 & 0.9998 \\ 
  truth & 0.5000 & 0.7486 & 0.7995 & 0.8997 & 0.9505 & 0.9898 & 0.9951 & 0.9990 & 0.9999 \\ 
   \hline
\end{tabular}
\caption{Monte Carlo estimation} 
\label{MC result}
\end{table}

## Boxplots of bias

Repeat the above expriment 100 times and plot bias of Monte Carlo methods at 
every time point $t$ using boxplots.

```{r Homework2_2}
library(ggplot2)
nsim <- 100
bias <- data.frame(bias = rep(0, nsim * length(t) * length(n)), 
                   t = rep(t, length(n) * nsim), 
                   n = rep(rep(n, each = length(t)), nsim))
for (i in 1:nsim) {
  phi.hat <- phi.MC(n, t)
  bias$bias[((i-1)*length(t)*length(n)+1):(i*length(t)*length(n))] <- 
    as.vector(t(phi.hat[1:length(n), ]) - phi.hat[length(n) + 1, ])
}
bias$t <- as.factor(bias$t)
ggplot(data = bias, aes(x = t, y = bias)) + geom_boxplot(outlier.colour="red", outlier.shape=8, outlier.size=4) + facet_wrap( ~ n)
```

